Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

### 2017-11-03 paper/galsize_paper.tex
Finished discussion of lensing prediction in section 4.5

@@

%---------------------------------------------------------------------------------------------------
\begin{figure}
\centering
\includegraphics[width=8cm]{FIGS/rvir_only_lensing_prediction.pdf}
\caption{
{\bf Prediction for $\rhalf-$dependence of galaxy lensing.}
Using the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}, we make predictions for as-yet-unseen measurements of the $\rhalf-$dependence of galaxy lensing of $\mstar-$complete samples. To date, the $\rhalf-$dependence of $\Delta\Sigma$ has only been measured for color-selected samples \citep{charlton_etal17}, in which the reverse is true: for both blue and red samples, $\Delta\Sigma$ of small galaxies is (weakly) suppressed relative to large galaxies. As a generic consequence of satellites being smaller than centrals of the same mass, we predict that the analogous measurement for $\mstar-$complete samples will show $\Delta\Sigma$ of small galaxies to be much stronger relative to large galaxies of the same stellar mass.
}
\label{fig:strippingorphans}
\end{figure}
%-----------------------------------------------------------------------------------------------------

>>>>

The $\rhalf-$dependence of galaxy lensing has recently been measured using CFHTLenS observations \citep{heymans_etal12,erben_etal13}. For both red- and blue-sequence galaxies, it was found in \citet{charlton_etal17} that the lensing signal, $\Delta\Sigma,$ of large galaxies is slightly stronger relative to smaller galaxies. This result is in good agreement with the clustering measurements in the top panels of Figure \ref{fig:colorclustering}, which show the same trend. To date, the $\rhalf-$dependence of $\Delta\Sigma$ not yet been measured for $\mstar-$complete samples. We show  predictions of the $\rvir-$based model for future measurements of this signal in Figure \ref{fig:lensingprediction}. The halo model explanation for this trend is the same as for $\wproj:$ satellites occupy higher mass host halos relative to centrals of the same stellar mass, boosting $\Delta\Sigma$ for small relative to large galaxy samples.

@@

%---------------------------------------------------------------------------------------------------
\begin{figure}
\centering
\includegraphics[width=8cm]{FIGS/rvir_only_lensing_prediction.pdf}
\caption{
{\bf Prediction for $\rhalf-$dependence of galaxy lensing.}
Using the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}, we make predictions for as-yet-unseen measurements of the $\rhalf-$dependence of galaxy lensing of $\mstar-$complete samples. To date, the $\rhalf-$dependence of $\Delta\Sigma$ has only been measured for color-selected samples \citep{charlton_etal17}, in which the reverse is true: for both blue and red samples, $\Delta\Sigma$ of small galaxies is (weakly) suppressed relative to large galaxies. As a generic consequence of satellites being smaller than centrals of the same mass, we predict that the analogous measurement for $\mstar-$complete samples will show $\Delta\Sigma$ of small galaxies to be much stronger relative to large galaxies of the same stellar mass.
}
\label{fig:lensingprediction}
\end{figure}
%-----------------------------------------------------------------------------------------------------
